15yrsChange

### 2024-04-05 doc/15yrsChange.Rmd
tweaks to recruitment paragraph

Relying on the current understory as a proxy for future canopy presents challenges.
White-tailed deer populations have varied greatly over the last century [@hanberry_regaining_2020].
Moreover, some canopy species, including some *Quercus* spp., are hypothesized to recruit in synchronized pulse events [@koenig_brief_2021].
A decline in deer population that reduces browsing pressure and coincides with a recruitment pulse could allow for substantial, rapid regeneration of canopy species.
However, current recruitment levels are below a rate which we would expect in maturing secondary forests.
When overlaid with increasing mortality, regeneration may be insufficient to prevent extended periods without a closed canopy.

>>>>

Similarly, a complex chain of processes -- from seed production to germination and seedling survival -- affects sapling recruitment, and relying on the current understory as a proxy for future canopy presents challenges.
Some canopy species, including some *Quercus* spp., are hypothesized to recruit in synchronized pulse events [@koenig_brief_2021].
Moreover, white-tailed deer populations have varied greatly over the last century [@hanberry_regaining_2020], and a decline in deer population that reduces browsing pressure and coincides with a recruitment pulse could allow for substantial, rapid regeneration of canopy species.
However, current recruitment levels are below a rate which we would expect in maturing secondary forests.
When overlaid with increasing mortality, regeneration is likely to be insufficient to prevent extended periods without a closed canopy.
